module2graphsandPCA

### 2022-03-15 module2graphsandPCA.Rmd
added headers to the HTML document and some formatting

---
title: "module2graphsandPCA"
output:
  html_document:
    fig_width: 7
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged
---

@@

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
moduletwo <- read_excel( "~/Desktop/thesis_surveydata/political_factors_complete.xlsx")
save(moduletwo, file = "moduletwo.rda")
module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
module2 %>%
  filter(!row_number() %in% c(1,2))

@@

@@

Q1. Below is a list of various centrally managed sources of energy. How risky are each of these energy technologies according to you?  Please tell me whether you see each technology as: not at all risky, slightly risky, moderately risky, very risky, or extremely risky

@@

Q2. Following is a list of various individually or community-owned and managed sources of energy. How risky are each of these energy technologies according to you? Please tell me whether you see each technology as: not at all risky, slightly risky, moderately risky, very risky, or extremely risky.

@@

Q3. Following is a list of centrally managed sources of energy. How beneficial are each of these according to you? Please tell me whether you see each technology as: not at all beneficial, slightly beneficial, moderately beneficial, very beneficial, or extremely beneficial?

@@

Q4. Following is a list of various individually or community owned and managed sources of energy. How beneficial are each of these according to you? Please tell me whether you see each technology as: not at all beneficial, slightly beneficial, moderately beneficial, very beneficial or extremely beneficial ?

@@

Principal Component Analysis on Kahan et al (2007) scale

K_IINTRFER	The government interferes far too much in our everyday lives.
K_IPRIVACY	The government should stop telling people how to live their lives.
K_SHARM	    Sometimes the government needs to make laws that keep people from hurting themselves.
K_IPROTECT	It’s not the government’s business to try to protect people from themselves.
K_SLIMCHOI	The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.
K_SPROTECT	The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.
K_HEQUAL	  We have gone too far in pushing equal rights in this country.
K_HREVDIS1	Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits.
K_EDISCRIM	Discrimination against minorities is still a very serious problem in our society.
K_ERADEQ1	  We need to dramatically reduce inequalities between the rich and the poor.
K_EWEALTH	  Our society would be better off if the distribution of wealth was more equal.
K_ERADEQ2	  We need to dramatically reduce inequalities between men and women.

@@

PCA on the economic -political values of the perceiver

DECISIONDECEN	 Local politicians shouldn't have to ask permission from the central government to implement policies
DECISIONCEN	   Laws and policies would be implemented more smoothly if more power lay with the central government.
SYSTEMTOTAL	   It is good to have a strong leader who does not have to bother with elections.
SYSTEMTECHNO	 Experts, not the government, should make decisions according to what they think is best for the country.
SYSTEMDEMO	   It is very important to have a democratic political system because it ensures that no individual leader has too much power.
SYSTEMRELIGION There should be a system governed by religious law.
INDUSTRYSMALL	 Large corporations are destroying the local industries in India and benefiting only a handful of people.
INDUSTRYLARGE	 Large scale industries are required for the development of the country that will benefit everyone
ECONOMYLOCAL	 India would be better off if foreign companies didn't come to here
ECONOMYGLOBAL	 Foreign companies have led to a range of benefits for the Indian people and society
DEVOVERENV	   Economic growth and creating jobs should be prioritized over environmental protection
ENVOVERDEV	   Polluting industries that spoil the environment should be shut down even if it costs people their jobs
OWNERPVT	     All businesses and industries should be owned privately
OWNERPUB	     The government should own most large businesses and industries
OWNERREG	     Regardless of ownership, the government should pass strong regulations and implement them
OWNERNOREG	   There is too much red-tape and the government should not interfere with businesses and industries
WEALTHLIM	     A limit should be put to how much wealth a person can amass
MECHANISATION	 Rapid mechanization of work is taking away jobs from workers in this country

@@

PCA on eco-pol characteristics of the technology -  Solar Energy

DISPLACESOLAR	 Solar energy is leading to displacement of people from their land
POLLUTESOLAR	 Solar energy increases pollution of air/water/land
HEALTHSOLAR	   Solar energy poses a great risk to the health of people living around it
JOBSSOLAR	     Solar energy will bring jobs to the local community
BEAUTYSOLAR	   Solar energy spoils the natural beauty of the landscape
PRIDESOLAR	   I would be proud if my community used solar energy
NPRIDESOLAR	   Solar energy is a mark of pride for our nation
DEVSOLAR	     Solar energy pushes forward the country's development
PROSPERSOLAR	 Solar energy brings economic prosperity to the surrounding regions
RELYSOLAR	     I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy

```{r}

@@

PCA on eco-pol characteristics of the technology -  Nuclear Energy

>>>>

---
title: "module2graphsandPCA"
output:
  html_document:
    fig_width: 10
    fig_height: 7
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged
---

@@

## Original Dataset
```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
moduletwo <- read_excel( "~/Desktop/thesis_surveydata/political_factors_complete.xlsx")
save(moduletwo, file = "moduletwo.rda")
module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
module2 %>%
  filter(!row_number() %in% c(1,2))

@@

## Coded Dataset

@@

## Q1. Below is a list of various centrally managed sources of energy. How risky are each of these energy technologies according to you?  Please tell me whether you see each technology as: not at all risky, slightly risky, moderately risky, very risky, or extremely risky

@@

## Q2. Following is a list of various individually or community-owned and managed sources of energy. How risky are each of these energy technologies according to you? Please tell me whether you see each technology as: not at all risky, slightly risky, moderately risky, very risky, or extremely risky.

@@

## Q3. Following is a list of centrally managed sources of energy. How beneficial are each of these according to you? Please tell me whether you see each technology as: not at all beneficial, slightly beneficial, moderately beneficial, very beneficial, or extremely beneficial?

@@

## Q4. Following is a list of various individually or community owned and managed sources of energy. How beneficial are each of these according to you? Please tell me whether you see each technology as: not at all beneficial, slightly beneficial, moderately beneficial, very beneficial or extremely beneficial ?

@@

## Principal Component Analysis on Kahan et al (2007) scale

- **K_IINTRFER**	The government interferes far too much in our everyday lives.
- **K_IPRIVACY**	The government should stop telling people how to live their lives.
- **K_SHARM**	    Sometimes the government needs to make laws that keep people from hurting themselves.
- **K_IPROTECT**	It’s not the government’s business to try to protect people from themselves.
- **K_SLIMCHOI**	The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.
- **K_SPROTECT**	The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.
- **K_HEQUAL**	  We have gone too far in pushing equal rights in this country.
- **K_HREVDIS1**	Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits.
- **K_EDISCRIM**	Discrimination against minorities is still a very serious problem in our society.
- **K_ERADEQ1**	  We need to dramatically reduce inequalities between the rich and the poor.
- **K_EWEALTH**	  Our society would be better off if the distribution of wealth was more equal.
- **K_ERADEQ2**	  We need to dramatically reduce inequalities between men and women.

@@

## PCA on the economic -political values of the perceiver

- **DECISIONDECEN**	 Local politicians shouldn't have to ask permission from the central government to implement policies
- **DECISIONCEN**	   Laws and policies would be implemented more smoothly if more power lay with the central government.
- **SYSTEMTOTAL**	   It is good to have a strong leader who does not have to bother with elections.
- **SYSTEMTECHNO**	 Experts, not the government, should make decisions according to what they think is best for the country.
- **SYSTEMDEMO**	   It is very important to have a democratic political system because it ensures that no individual leader has too much power.
- **SYSTEMRELIGION** There should be a system governed by religious law.
- **INDUSTRYSMALL**	 Large corporations are destroying the local industries in India and benefiting only a handful of people.
- **INDUSTRYLARGE**	 Large scale industries are required for the development of the country that will benefit everyone
- **ECONOMYLOCAL**	 India would be better off if foreign companies didn't come to here
- **ECONOMYGLOBAL**	 Foreign companies have led to a range of benefits for the Indian people and society
- **DEVOVERENV**	   Economic growth and creating jobs should be prioritized over environmental protection
- **ENVOVERDEV**	   Polluting industries that spoil the environment should be shut down even if it costs people their jobs
- **OWNERPVT**	     All businesses and industries should be owned privately
- **OWNERPUB**	     The government should own most large businesses and industries
- **OWNERREG**	     Regardless of ownership, the government should pass strong regulations and implement them
- **OWNERNOREG**	   There is too much red-tape and the government should not interfere with businesses and industries
- **WEALTHLIM**	     A limit should be put to how much wealth a person can amass
- **MECHANISATION**	 Rapid mechanization of work is taking away jobs from workers in this country

@@

## PCA on eco-pol characteristics of the technology -  Solar Energy

- **DISPLACESOLAR**	 Solar energy is leading to displacement of people from their land
- **POLLUTESOLAR**	 Solar energy increases pollution of air/water/land
- **HEALTHSOLAR**	   Solar energy poses a great risk to the health of people living around it
- **JOBSSOLAR**	     Solar energy will bring jobs to the local community
- **BEAUTYSOLAR**	   Solar energy spoils the natural beauty of the landscape
- **PRIDESOLAR**	   I would be proud if my community used solar energy
- **NPRIDESOLAR**	   Solar energy is a mark of pride for our nation
- **DEVSOLAR**	     Solar energy pushes forward the country's development
- **PROSPERSOLAR**	 Solar energy brings economic prosperity to the surrounding regions
- **RELYSOLAR**	     I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy

@@

## PCA on eco-pol characteristics of the technology -  Nuclear Energy
